Attributions for Poverty in Post-Socialist Countries

### 2014-02-12 article2013.Rmd
Poistin eriarvoisuus+maaryhmaläpän ja lisäsin melko lopulliset kuviot&taulukot. Esitän tän Mikolle2

---
title: Attributions for Poverty in Post-Socialist Countries
author: [Markus Kainu & Mikko Niemelä]
date: February 11, 2014
abstract: Utilising The Life in Transition Survey (LiTS) conducted in 2010, the purpose of the paper is to examine public perceptions of the causes of poverty in Europe and Western Asia with special emphasis on post-socialist countries. The study applies multilevel techniques in order to analyse the role of individual and country-level explanatory factors as determinants of poverty attributions. As country-level determinants, paper analyses the changes in country's economic performance during the period of global financial crises, income inequality and the state of democracy. As individual-level determinants, the paper tests to what extent risk factors related to financial hardship are associated with perceptions of the causes of poverty.
keywords: poverty
output:
  pdf_document:
    toc: true
    number_section: true
    highlight: zenburn
  html_document:
    toc: true
    theme: flatly
---

@@

There are also considerable differences in other aspects of socio-political context between examined countries. One of these aspects is the extent of income inequality which varies extensively between examined countries. Thus, this study examines the role of income inequality as a contextual-level explanatory factor of public perceptions of the causes of poverty. The link between inequality and attributions for poverty is not that easy to predict. One the one hand, the public in countries with greater inequality is more inclined to mistrust “others” (e.g. Uslander, 2002). Therefore, the uneven distribution of wealth should mean stronger support for the individualistic explanation for poverty. On the other hand, cross-national studies on attributions for poverty have shown that the support for the individual blame is lower in countries with lower level of income inequality (e.g. Gallie and Paugam, 2002; Kallio and Niemelä, 2013).

@@

Gini coefficient                  Measures the distribution of income or consumption expenditure among individuals or households                World Bank

Voice and Accountability          Indicators measuring the political process, civil liberties and political rights.                             World Bank
----------------------------

@@

<!--

![Gini coefficient and support for social (top) and individual (bottom) blame types of attributions for poverty](figure/scatter_gini.pdf)

-->

![**Perceived inequality from data** and support for social (top) and individual (bottom) blame types of attributions for poverty](figure/scatter_perGini.pdf)

>There is also a substantial variation in the level of income inequality among post-socialist countries. Figure 3 shows that the higher level of income inequality is associated with higher level of social blame. As for individual blame type of explanation the picture is more puzzled, showing only weak connection between larger inequality and lower support for individual blame explanation. Again, the Western European countries differ with post-socialist countries. Cross-national differences in income inequality are much smaller in Western Europe than among post-socialist countries. There is a weak negative association between the social blame and income  inequality and a strong positive association between the individual blame and income inequality.

![**Perceived inequality from data** and support for social (top) and individual (bottom) blame types of attributions for poverty](figure/scatter_perGini.pdf)

@@

AND SOMETHING ABOUT THE NEW FIGURE ON HUMAN DEVELPMENT INDEX AND LIVING CONDITIONS OF THE PEOPLE AND SKIPPING THE NEXT PARAGRAPH ON INEQUALITY

>There is also a substantial variation in the level of income inequality among post-socialist countries. Figure 3 shows that the higher level of income inequality is associated with higher level of social blame. As for individual blame type of explanation the picture is more puzzled, showing only weak connection between larger inequality and lower support for individual blame explanation. Again, the Western European countries differ with post-socialist countries. Cross-national differences in income inequality are much smaller in Western Europe than among post-socialist countries. There is a weak negative association between the social blame and income  inequality and a strong positive association between the individual blame and income inequality.

>>>>

---
title: Attributions for Poverty in Post-Socialist Countries
author: [Markus Kainu & Mikko Niemelä]
date: February 12, 2014
abstract: Utilising The Life in Transition Survey (LiTS) conducted in 2010, the purpose of the paper is to examine public perceptions of the causes of poverty in Europe and Western Asia with special emphasis on post-socialist countries. The study applies multilevel techniques in order to analyse the role of individual and country-level explanatory factors as determinants of poverty attributions. As country-level determinants, paper analyses the changes in country's economic performance during the period of global financial crises, income inequality and the state of democracy. As individual-level determinants, the paper tests to what extent risk factors related to financial hardship are associated with perceptions of the causes of poverty.
keywords: poverty
output:
  pdf_document:
    toc: true
    number_section: true
---

@@

----

*Eriarvoisuus lähti tästä*

*Maaryhmittely on tästä pois*

**Tähän tulisi HDI:n/elinolojen perustelut**

----

@@

Human Development Index           Measures life expectancy, education, and income indices as a composite statistic
UNDP

Voice and Accountability          Indicators measuring the political process, civil liberties and political rights                             World Bank
----------------------------

@@

@@

HERE WE NEED AN INTREPETATIIONS OF HDI-FIGURE. BUT THE RESOURCES FIRST

### 2014-02-12 index.Rmd
Etusivu päivitetty..
Getting back to business. Nothing changed, but rerunning the script.
Poistin eriarvoisuus+maaryhmaläpän ja lisäsin melko lopulliset kuviot&taulukot. Esitän tän Mikolle2

| html-ouput | source code |
| ------------ | -------------- |
| [loading, cleaning and summarizing](loadClean.html) | [source](loadClean.Rmd) |

@@

| html-ouput | source code |
| ------------ | -------------- |
| [Descriptive analysis](descriptive_analysis.html) | [source](descriptive_analysis.Rmd) |
| [Spatial visualization](mapPlots.html) | [source](mapPlots.Rmd) |
| [Graphics in the paper](finalPlots.html) | [source](finalPlots.Rmd) |

@@

| html-ouput | source code |
| ------------ | -------------- |
| [Regression analysis](regressionModelling.html) | [source](regressionModelling.Rmd) |

@@

| pdf-ouput | source code |
| ------------ | -------------- |
| [Article draft in .pdf](article2013.pdf) | [source](article2013.Rmd) |

@@

- [HSE Moscow - November 12, 2013](moscow2013/lcsr20131112.html)
- [Jatkokoulutusseminaari Turku November 7, 2013](turku2013/slidesTkuJatko20131107.html)
- [ESA Torino - August 29, 2013](torino2013/TorinoSlides2013_final.html)

# Misc links

- [Article code in github](https://github.com/muuankarski/attributions)
- [rustfare-package](http://markuskainu.fi/rustfare/) *- toolbox for R language for open welfare data from Russian Federation*
- [rOpenGov](http://ropengov.github.io/) *-  R Ecosystem for Open Government Data and Computational Social Science*
- [markuskainu.fi](http://markuskainu.fi) *- personal website*

-----

>>>>

| html-ouput | source code |
| ------------ | -------------- |
| [loading, cleaning and summarizing](http://muuankarski.github.io/attributions/loadClean.html) | [source](http://muuankarski.github.io/attributions/loadClean.Rmd) |

@@

| html-ouput | source code |
| ------------ | -------------- |
| [Descriptive analysis](http://muuankarski.github.io/attributions/descriptive_analysis.html) | [source](http://muuankarski.github.io/attributions/descriptive_analysis.Rmd) |
| [Spatial visualization](http://muuankarski.github.io/attributions/mapPlots.html) | [source](http://muuankarski.github.io/attributions/mapPlots.Rmd) |
| [Graphics in the paper](http://muuankarski.github.io/attributions/finalPlots.html) | [source](http://muuankarski.github.io/attributions/finalPlots.Rmd) |

### Misc analysis

| html-ouput | source code |
| ------------ | -------------- |
| [Comparing waves 2006 and 2011](http://muuankarski.github.io/attributions/compareWaves.html) | [source](http://muuankarski.github.io/attributions/compareWaves.Rmd) |
| [Exploring the macro level correlations](http://muuankarski.github.io/attributions/correlations.html) | [source](http://muuankarski.github.io/attributions/correlations.md) |

@@

| html-ouput | source code |
| ------------ | -------------- |
| [Regression analysis](http://muuankarski.github.io/attributions/regressionModelling.html) | [source](http://muuankarski.github.io/attributions/regressionModelling.Rmd) |

@@

| pdf-ouput | source code |
| ------------ | -------------- |
| [Article draft in .pdf](http://muuankarski.github.io/attributions/article2013.pdf) | [source](http://muuankarski.github.io/attributions/article2013.Rmd) |

@@

- [slides](http://muuankarski.github.io/attributions/attrib_slides.html)
